Pool Model Paper

### 2023-12-06 pool_model.tex
Add descriprion to plots for 3 pool model and temp shift

Motivated by this we divide a bacterial population into three pools (states) (\textbf{Figure \ref{fig:SchematicRep}}): 

@@

For simplicity we rather make a transition to the dimensionless constant $\alpha:=\alpha_0 N_t$ and diminsioneless resource pool $R(t) = R_0 / N_t$ ($0 \leqslant R \leqslant 1$).

@@

Such model can be simplified by explointing that limitation of the resource pool also limits the total bacterial count of the system:

@@

         \mu & + \mu'& - \beta 

@@

@@

If yes, the three pool model would be advantageous, if not the two pool model is sufficient with the advantages of having one parameter less.

@@

        The other model parameters are $\alpha=2.5$, $\mu'=0.5$, $\beta=5$, $\lambda=10^{-2}$, $\mu = 0$ fe each curve.

@@

@@

Further we show that the TPM can be readily extended to the systems with more than one bacteria and describe more complex relationships between species. 

@@

One on the ways to describe competition between bacteria populations is as a function of limiting resources ratio~\cite{tilman_resource_1977, smith_effects_2002}.

>>>>

Motivated by this we divide a bacterial population into three pools (states) (Figure~\ref{fig:SchematicRep}): 

@@

For simplicity we rather make a transition to the dimensionless constant $\alpha:=\alpha_0 N_t$ and diminsionless resource pool $R(t) = R_0 / N_t$ ($0 \leqslant R \leqslant 1$).

@@

Such model can be simplified by exploiting that limitation of the resource pool also limits the total bacterial count of the system:

@@

         \mu &  \mu'& - \beta 

@@

The resulting growth curves for the three pool case are presented in Figure~\ref{fig:3pool_resource_plots}.
Here we can see that the value of the transition constant $\lambda$ determines how long the bacteria is in lag-phase.
The larger is the rate the shorter is the lag-time.
Moreover, by including the bacteria flow to the death pool we can diversify the shape of the growth curve allowing the decrease of the bacterial count.

@@

If yes, the three pool model would be advantageous, if not the two pool model is sufficient with the advantages of having one parameter less.\\

@@

        The other model parameters are $\alpha=2.5$, $\mu'=0.5$, $\beta=5$, $\lambda=10^{-2}$, $\mu = 0$ for each curve.

@@

The effect of the temperature shift on the total bacterial count can be shown in Figure~\ref{fig:TempJump}.
After the rapid temperature increase, the growth slows down till the bacteria that transitioned back to lag-phase go again to growth pool.
If the shift happened rather early in time, when most of the bacteria were in lag-phase, the effect is not noticeable.

@@

Further we show that the TPM can be readily extended to the systems with more than one bacterium and describe more complex relationships between species. 

@@

One on the ways to describe competition between bacteria populations is as a function of limiting resource ratio~\cite{tilman_resource_1977, smith_effects_2002}.
